quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-15 paper-quollr.Rmd
Added updated benchmark function

- dependancies
- basic example

@@

@@

```{r}
tour1 <- show_langevitour(df_all, df_bin, df_bin_centroids, benchmark_value = benchmark,
                          distance = distance, distance_col = distance)
tour1
```

>>>>

- dependancies

```{r, eval=FALSE}
library(tools)
package_dependencies("quollr")
```

- basic example

@@

If shift_x happen to the positive direction of x it should input as a positive value, if not other way
If shift_y happen to the positive direction of y it should input as a positive value, if not other way

@@

```{r}
tour1 <- show_langevitour(df_all, df_bin, df_bin_centroids, benchmark_value = benchmark,
                          distance = distance, distance_col = "distance")
tour1
```

### 2024-02-15 paper-quollr.tex
Added updated benchmark function

\begin{itemize}
\tightlist
\item
  dependancies
\item
  basic example
\end{itemize}

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-5-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-10-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-16-1.pdf}

@@

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-23-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-29-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-34-1.pdf}

@@

\begin{verbatim}
tour1 <- show_langevitour(df_all, df_bin, df_bin_centroids, benchmark_value = benchmark,
                          distance = distance, distance_col = distance)
tour1
\end{verbatim}

>>>>

\begin{itemize}
\tightlist
\item
  dependancies
\end{itemize}

\begin{verbatim}
library(tools)
package_dependencies("quollr")
\end{verbatim}

\begin{itemize}
\tightlist
\item
  basic example
\end{itemize}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-8-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-12-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-18-1.pdf}

@@

If shift\_x happen to the positive direction of x it should input as a positive value, if not other way
If shift\_y happen to the positive direction of y it should input as a positive value, if not other way

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-25-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-31-1.pdf}

@@

@@

\begin{verbatim}
tour1 <- show_langevitour(df_all, df_bin, df_bin_centroids, benchmark_value = benchmark,
                          distance = distance, distance_col = "distance")
tour1
\end{verbatim}

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-39-1.pdf}
